Detecting Facial Expressions in Professional Tennis Matches

### 2017-08-29 Report06-12.Rmd
Minor text edits

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)

@@

##Software Selection
The choice of the initial software considered for this research were informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'

@@

From the software's analysed we considered availability for use within the time frame of the report. This led us to choose Animetrics FaceR. The report outlines that for Animetrics, 'one requirement is that image/face proportion
should be at least 1:8 and that at least 64 pixels between eyes are required'. We realize this could present challenges given our data set.
It will also allow for an extension from detecting to recognizing people in the data set.

@@

colnames(players)
```
When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(kfigr)
library(UpSetR)
library(descr)
library(xtable)
library(gtable)
library(ggthemes)
library(EBImage)

@@

##Software Selection
The choice of the initial software considered for this research was informed by a report that reviewed 'commercial off-the-shelf (COTS) solutions and related patents for face recognition in video surveillance applications.'

@@

From the software analysed we considered availability for use within the time frame of the report. This led us to choose Animetrics FaceR. The report outlines that for Animetrics, 'one requirement is that image/face proportion
should be at least 1:8 and that at least 64 pixels between eyes are required'. We realize this could present challenges given our data set.
It will also allow for an extension from detecting to recognizing people in the data set.

@@

```
When forcing no intercept, all variables are significant at the 0 level, and obscured is only significant at the 0.001 level.
